---
title: 'Assignment 1: R Markdown practice'
author: "Ghaun Kim"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: yes
    dev: pdf
    highlight: tango
  html_document:
    theme: paper
    self_contained: yes
    toc: no
    df_print: kable
    fig_caption: no
    number_sections: yes
    smart: yes
    dev: svg
  word_document:
    toc: no
geometry: margin=1in
fontsize: 11pt
documentclass: article
urlcolor: blue
---
<!-- Write your Markdown below this line -->
# Section 1
**Section K01**

# Course Goals 

By the end of the course, students will be able to:

- Use [Github](https://github.com) for creating a reproducible research document.
     
     -- My Github Username is: *gkim44*
     
- Obtain, clean, transform, and visualize a dataset using the R programming language.
- Interpret and predict dataset trends using statistical inference and models.
- Critically examine and interpret statistical claims reported in mass media.

# Including Code

## Running R code in a code chunk

```{r}
x <- 2+2
x+3
```
The output of first line of code is not printed out because it is assigned to a variable instead.

The second line of output is printed out instead, but this means that the calculated value has notbeen saved for future use.

## Displaying Graphs
```{r}
ggplot2::qplot(data = iris, x = Sepal.Length, y = Sepal.Width)
```



  

